\makeatletter
\renewcommand*\cleardoublepage{\clearpage\if@twoside
  \ifodd\c@page \hbox{}\newpage\if@twocolumn\hbox{}%
  \newpage\fi\fi\fi}
\makeatother

\chapter*{Introduction}

Mutual Muses is a crowdsourced transcription project undertaken by the Digital Art History program at the Getty Research Institute in 2017. The project crowdsourced transcriptions of correspondence from the archives of art critic Lawrence Alloway (1926-1990) and feminist artist Sylvia Sleigh (ca. 1916-2010), which are held at the Getty Research Institute in Los Angeles. These letters reveal the intimate early stages of their respective professional careers and intertwined personal lives in postwar England from 1948-1953. The results of this project included transcription data for 2,376 documents from these archives.

Documents are organized by year of correspondence and contain image files and corresponding transcriptions. The document is best viewed as a two-page spread using a PDF reader.

The transcription data are offered under a Creative Commons CC0 1.0 Universal Public Domain Dedication. See: \url{https://creativecommons.org/publicdomain/zero/1.0/}.

The J. Paul Getty Trust also owns the copyright to the Lawrence Alloway and Sylvia Sleigh papers, including digital images of the correspondence. These images are not included under any open license.

This publication uses data generated via the \href{https://www.zooniverse.org/}{Zooniverse.org} platform, development of which is funded by generous support, including a Global Impact Award from Google, and by a grant from the Alfred P. Sloan Foundation. Zooniverse is an open-source, ``citizen science'' platform that facilitates collaboration between volunteers and researchers working on data collection research projects.
